---
title: "Study 3 Data Analysis"
author: ""
date: "Updated 02/13/2024"
output:
  html_document:
    number_sections: no
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no
  pdf_document:
    toc: yes
    toc_depth: '3'
theme: sandstone
highlight: tango
---

```{r, echo=FALSE, message= FALSE, warning= FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(rstatix)
library(lubridate)
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(ggExtra)
library(tidyr)
library(plyr)
library(plotly)
library(dplyr)
library(psych)
library(psycho)
library(tidyboot)
library(FactoMineR)
library(factoextra)
library(stringr)
library(formattable)
library(factoextra)
library(usmap)
library(alphaOutlier)
library(Rmisc)
library(mediation)
library(lme4)
library(lmerTest)
library(emmeans)
library(car)
library(mediation)
library(lsr)
library(kableExtra)
library(multcomp)
library(irr)
library(effsize)
library(showtext) 
library(ltm)
library(ggpattern)

#Put file path to Study3Data.csv below:
df <- read.csv("~/CCR_Scale/CCR_Scale_Study_1-3_Data_Analysis/Study_3/Study3Data.csv", header=T)

#Create a factor for attitude
df$condition <- factor(
  df$condition,
  levels = 1:2,
  labels = c("Responsive", "Unresponsive")
)

#Put file path to Study3QualitativeData.csv below:
df_coding <- read.csv("~/CCR_Scale/CCR_Scale_Study_1-3_Data_Analysis/Study_3/Study3QualitativeData.csv", header=T)

#Create a factor for attitude
df_coding$condition <- factor(
  df_coding$condition,
  levels = 1:2,
  labels = c("Responsive", "Unresponsive")
)

```

## Connection-Coordination Rapport (CCR) Scale

#### Connection-Coordination Rapport (CCR) Scale {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}


summarySE <- summarySE(df, measurevar="rapport_score", groupvars=c("condition"), na.rm = TRUE)
plot <- ggplot(data=summarySE, aes(x=condition, y=rapport_score)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5) +
geom_errorbar(aes(ymin=rapport_score-se, ymax=rapport_score+se),width=.2, position=position_dodge(.5)) +
xlab("Condition") +
ggtitle("Connection-Coordination Rapport (CCR) Scale") +
theme_bw()+   
coord_cartesian(ylim = c(1, 5))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$rapport_score,
df["condition"],
function(x) mean(x, na.rm = TRUE)
)

sds <- aggregate(
df$rapport_score,
df["condition"],
function(x) sd(x, na.rm = TRUE)
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Responsive", "Unresponsive")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### independent-sample t-test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Perform independent-sample t-test
t_test_result <- t.test(rapport_score ~ condition, data = df, var.equal = TRUE)

# View the results
print(t_test_result)


```

##### calculate Cohen’s d and 95% CI for Cohen’s d

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Calculate Cohen's d
cohen_d <- cohen.d(rapport_score ~ condition, data = df, hedges.correction = TRUE)
print(cohen_d)

```

## Connection Factor in CCR Scale

#### Connection Factor in CCR Scale {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}


summarySE <- summarySE(df, measurevar="rapport_connection_factor_score", groupvars=c("condition"), na.rm = TRUE)
plot <- ggplot(data=summarySE, aes(x=condition, y=rapport_connection_factor_score)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5) +
geom_errorbar(aes(ymin=rapport_connection_factor_score-se, ymax=rapport_connection_factor_score+se),width=.2, position=position_dodge(.5)) +
xlab("Condition") +
ggtitle("Connection Factor in CCR Scale") +
theme_bw()+   
coord_cartesian(ylim = c(1, 5))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$rapport_connection_factor_score,
df["condition"],
function(x) mean(x, na.rm = TRUE)
)

sds <- aggregate(
df$rapport_connection_factor_score,
df["condition"],
function(x) sd(x, na.rm = TRUE)
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Responsive", "Unresponsive")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### independent-sample t-test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Perform independent-sample t-test
t_test_result <- t.test(rapport_connection_factor_score ~ condition, data = df, var.equal = TRUE)

# View the results
print(t_test_result)


```

##### calculate Cohen’s d and 95% CI for Cohen’s d

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Calculate Cohen's d
cohen_d <- cohen.d(rapport_connection_factor_score ~ condition, data = df, hedges.correction = TRUE)
print(cohen_d)

```

## Coordination Factor in CCR Scale

#### Coordination Factor in CCR Scale {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}


summarySE <- summarySE(df, measurevar="rapport_coordination_factor_score", groupvars=c("condition"), na.rm = TRUE)
plot <- ggplot(data=summarySE, aes(x=condition, y=rapport_coordination_factor_score)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5) +
geom_errorbar(aes(ymin=rapport_coordination_factor_score-se, ymax=rapport_coordination_factor_score+se),width=.2, position=position_dodge(.5)) +
xlab("Condition") +
ggtitle("Coordination Factor in CCR Scale") +
theme_bw()+   
coord_cartesian(ylim = c(1, 5))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$rapport_coordination_factor_score,
df["condition"],
function(x) mean(x, na.rm = TRUE)
)

sds <- aggregate(
df$rapport_coordination_factor_score,
df["condition"],
function(x) sd(x, na.rm = TRUE)
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Responsive", "Unresponsive")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### independent-sample t-test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Perform independent-sample t-test
t_test_result <- t.test(rapport_coordination_factor_score ~ condition, data = df, var.equal = TRUE)

# View the results
print(t_test_result)


```

##### calculate Cohen’s d and 95% CI for Cohen’s d

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Calculate Cohen's d
cohen_d <- cohen.d(rapport_coordination_factor_score ~ condition, data = df, hedges.correction = TRUE)
print(cohen_d)

```


## Perceived Robot Responsiveness

#### Perceived Robot Responsiveness {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

df$perceived_robot_responsiveness <- 
  (df$Q8_1+
  df$Q8_2+
  df$Q8_3+
  df$Q8_4+
  df$Q8_5+
  df$Q8_6+
  df$Q8_7+
  df$Q8_8+
  df$Q8_9)/9

# Specify the columns to calculate Cronbach's alpha
selected_columns <- df[, c("Q8_1", "Q8_2", "Q8_3","Q8_4", "Q8_5", "Q8_6", "Q8_7", "Q8_8", "Q8_9")]
cronbach.alpha(selected_columns)

summarySE <- summarySE(df, measurevar="perceived_robot_responsiveness", groupvars=c("condition"), na.rm = TRUE)
plot <- ggplot(data=summarySE, aes(x=condition, y=perceived_robot_responsiveness)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5) +
geom_errorbar(aes(ymin=perceived_robot_responsiveness-se, ymax=perceived_robot_responsiveness+se),width=.2, position=position_dodge(.5)) +
xlab("Condition") +
ggtitle("Perceived Robot Responsiveness") +
theme_bw()+   
coord_cartesian(ylim = c(1, 5))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$perceived_robot_responsiveness,
df["condition"],
function(x) mean(x, na.rm = TRUE)
)

sds <- aggregate(
df$perceived_robot_responsiveness,
df["condition"],
function(x) sd(x, na.rm = TRUE)
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Responsive", "Unresponsive")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### independent-sample t-test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Perform independent-sample t-test
t_test_result <- t.test(perceived_robot_responsiveness ~ condition, data = df, var.equal = TRUE)

# View the results
print(t_test_result)

```

##### calculate Cohen’s d and 95% CI for Cohen’s d

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Calculate Cohen's d
cohen_d <- cohen.d(perceived_robot_responsiveness ~ condition, data = df, hedges.correction = TRUE)
print(cohen_d)

```

## Perceived Robot Sociability

#### Perceived Robot Sociability {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

df$perceived_robot_sociability <- 
  (df$Q217_1+
  df$Q217_2+
  df$Q217_3+
  df$Q217_4)/4

# Specify the columns to calculate Cronbach's alpha
selected_columns <- df[, c("Q217_1", "Q217_2", "Q217_3","Q217_4")]
cronbach.alpha(selected_columns)

summarySE <- summarySE(df, measurevar="perceived_robot_sociability", groupvars=c("condition"), na.rm = TRUE)
plot <- ggplot(data=summarySE, aes(x=condition, y=perceived_robot_sociability)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5) +
geom_errorbar(aes(ymin=perceived_robot_sociability-se, ymax=perceived_robot_sociability+se),width=.2, position=position_dodge(.5)) +
xlab("Condition") +
ggtitle("Perceived Robot Sociability") +
theme_bw()+
coord_cartesian(ylim = c(1, 5))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$perceived_robot_sociability,
df["condition"],
function(x) mean(x, na.rm = TRUE)
)

sds <- aggregate(
df$perceived_robot_sociability,
df["condition"],
function(x) sd(x, na.rm = TRUE)
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Responsive", "Unresponsive")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### independent-sample t-test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Perform independent-sample t-test
t_test_result <- t.test(perceived_robot_sociability ~ condition, data = df, var.equal = TRUE)

# View the results
print(t_test_result)

```

##### calculate Cohen’s d and 95% CI for Cohen’s d

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Calculate Cohen's d
cohen_d <- cohen.d(perceived_robot_sociability ~ condition, data = df, hedges.correction = TRUE)
print(cohen_d)

```

## Perceived Robot Competence

#### Perceived Robot Competence {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}
df$perceived_robot_competence <- 
  (df$Q217_5+
  df$Q217_6+
  df$Q217_7+
  df$Q217_8)/4

# Specify the columns to calculate Cronbach's alpha
selected_columns <- df[, c("Q217_5", "Q217_6", "Q217_7","Q217_8")]
cronbach.alpha(selected_columns)

summarySE <- summarySE(df, measurevar="perceived_robot_competence", groupvars=c("condition"), na.rm = TRUE)
plot <- ggplot(data=summarySE, aes(x=condition, y=perceived_robot_competence)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5) +
geom_errorbar(aes(ymin=perceived_robot_competence-se, ymax=perceived_robot_competence+se),width=.2, position=position_dodge(.5)) +
xlab("Condition") +
ggtitle("Perceived Robot Competence") +
theme_bw()+
coord_cartesian(ylim = c(1, 5))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$perceived_robot_competence,
df["condition"],
function(x) mean(x, na.rm = TRUE)
)

sds <- aggregate(
df$perceived_robot_competence,
df["condition"],
function(x) sd(x, na.rm = TRUE)
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Responsive", "Unresponsive")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### independent-sample t-test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Perform independent-sample t-test
t_test_result <- t.test(perceived_robot_competence ~ condition, data = df, var.equal = TRUE)

# View the results
print(t_test_result)

```

##### calculate Cohen’s d and 95% CI for Cohen’s d

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Calculate Cohen's d
cohen_d <- cohen.d(perceived_robot_competence ~ condition, data = df, hedges.correction = TRUE)
print(cohen_d)

```


## Perceived Robot Attractiveness

#### Perceived Robot Attractiveness {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}
df$perceived_robot_attractiveness <- 
  (df$Q218_1+
  df$Q218_2+
  df$Q218_3+
  df$Q218_4+
  df$Q218_5+
  df$Q218_6)/6

# Specify the columns to calculate Cronbach's alpha
selected_columns <- df[, c("Q218_1", "Q218_2", "Q218_3","Q218_4", "Q218_5", "Q218_6")]
cronbach.alpha(selected_columns)

summarySE <- summarySE(df, measurevar="perceived_robot_attractiveness", groupvars=c("condition"), na.rm = TRUE)
plot <- ggplot(data=summarySE, aes(x=condition, y=perceived_robot_attractiveness)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5) +
geom_errorbar(aes(ymin=perceived_robot_attractiveness-se, ymax=perceived_robot_attractiveness+se),width=.2, position=position_dodge(.5)) +
xlab("Condition") +
ggtitle("Perceived Robot Attractiveness") +
theme_bw()+
coord_cartesian(ylim = c(1, 7))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$perceived_robot_attractiveness,
df["condition"],
function(x) mean(x, na.rm = TRUE)
)

sds <- aggregate(
df$perceived_robot_attractiveness,
df["condition"],
function(x) sd(x, na.rm = TRUE)
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Responsive", "Unresponsive")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### independent-sample t-test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Perform independent-sample t-test
t_test_result <- t.test(perceived_robot_attractiveness ~ condition, data = df, var.equal = TRUE)

# View the results
print(t_test_result)

```

##### calculate Cohen’s d and 95% CI for Cohen’s d

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Calculate Cohen's d
cohen_d <- cohen.d(perceived_robot_attractiveness ~ condition, data = df, hedges.correction = TRUE)
print(cohen_d)

```


## Participant's Desire for Robot Companionship

#### Participant's Desire for Robot Companionship {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

df$desire_for_robot_companionship <- 
  (df$Q219_1+
  df$Q219_2)/2

# Specify the columns to calculate Cronbach's alpha
selected_columns <- df[, c("Q219_1", "Q219_2")]
cronbach.alpha(selected_columns)

summarySE <- summarySE(df, measurevar="desire_for_robot_companionship", groupvars=c("condition"), na.rm = TRUE)
plot <- ggplot(data=summarySE, aes(x=condition, y=desire_for_robot_companionship)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5) +
geom_errorbar(aes(ymin=desire_for_robot_companionship-se, ymax=desire_for_robot_companionship+se),width=.2, position=position_dodge(.5)) +
xlab("Condition") +
ggtitle("Participant's Desire for Robot Companionship") +
theme_bw()+
coord_cartesian(ylim = c(1, 5))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$desire_for_robot_companionship,
df["condition"],
function(x) mean(x, na.rm = TRUE)
)

sds <- aggregate(
df$desire_for_robot_companionship,
df["condition"],
function(x) sd(x, na.rm = TRUE)
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Responsive", "Unresponsive")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### independent-sample t-test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Perform independent-sample t-test
t_test_result <- t.test(desire_for_robot_companionship ~ condition, data = df, var.equal = TRUE)

# View the results
print(t_test_result)

```

##### calculate Cohen’s d and 95% CI for Cohen’s d

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Calculate Cohen's d
cohen_d <- cohen.d(desire_for_robot_companionship ~ condition, data = df, hedges.correction = TRUE)
print(cohen_d)

```


## Participant's Approach Behaviors

#### Participant's Approach Behaviors {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

df_coding$behavioral <- (df_coding$behavioral_coder_2+df_coding$behavioral_coder_3)/2

summarySE <- summarySE(df_coding, measurevar="behavioral", groupvars=c("condition"), na.rm = TRUE)
plot <- ggplot(data=summarySE, aes(x=condition, y=behavioral)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5) +
geom_errorbar(aes(ymin=behavioral-se, ymax=behavioral+se),width=.2, position=position_dodge(.5)) +
xlab("Condition") +
ggtitle("Participant's Approach Behaviors") +
theme_bw()+
coord_cartesian(ylim = c(1, 5))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df_coding$behavioral,
df_coding["condition"],
function(x) mean(x, na.rm = TRUE)
)

sds <- aggregate(
df_coding$behavioral,
df_coding["condition"],
function(x) sd(x, na.rm = TRUE)
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Responsive", "Unresponsive")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### independent-sample t-test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Perform independent-sample t-test
t_test_result <- t.test(behavioral ~ condition, data = df_coding, var.equal = TRUE)

# View the results
print(t_test_result)

```

##### calculate Cohen’s d and 95% CI for Cohen’s d

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Calculate Cohen's d
cohen_d <- cohen.d(behavioral ~ condition, data = df_coding, hedges.correction = TRUE)
print(cohen_d)

```

## Participant's Self-disclosure

#### Participant's Self-disclosure {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

df_coding$disclosure <- (df_coding$disclosure_coder_2+df_coding$disclosure_coder_3)/2

summarySE <- summarySE(df_coding, measurevar="disclosure", groupvars=c("condition"), na.rm = TRUE)
plot <- ggplot(data=summarySE, aes(x=condition, y=disclosure)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5) +
geom_errorbar(aes(ymin=disclosure-se, ymax=disclosure+se),width=.2, position=position_dodge(.5)) +
xlab("Condition") +
ggtitle("Participant's Self-disclosure") +
theme_bw()+
coord_cartesian(ylim = c(1, 5))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df_coding$disclosure,
df_coding["condition"],
function(x) mean(x, na.rm = TRUE)
)

sds <- aggregate(
df_coding$disclosure,
df_coding["condition"],
function(x) sd(x, na.rm = TRUE)
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Responsive", "Unresponsive")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### independent-sample t-test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Perform independent-sample t-test
t_test_result <- t.test(disclosure ~ condition, data = df_coding, var.equal = TRUE)

# View the results
print(t_test_result)

```

##### calculate Cohen’s d and 95% CI for Cohen’s d

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Calculate Cohen's d
cohen_d <- cohen.d(disclosure ~ condition, data = df_coding, hedges.correction = TRUE)
print(cohen_d)

```

## Krippendorff’s Alpha for Participant’s Approach Behaviors and Participant’s Self-disclosure

#### Krippendorff’s Alpha {.tabset}

##### Video Coding

```{r, echo=FALSE, message= FALSE, warning= FALSE}

coded_data <-
  tribble(
    ~content_id, ~coder_id, ~behavior, ~disclosure,   
    4,           "Coder 1",       3,         5,
    5,           "Coder 1",       1,         2,  
    8,           "Coder 1",       3,         5,  
    12,          "Coder 1",       3,         5,  
    16,          "Coder 1",       4,         3,  
    4,           "Coder 2",       3,         5,  
    5,           "Coder 2",       1,         2,  
    8,           "Coder 2",       2,         5,  
    12,          "Coder 2",       3,         4,  
    16,          "Coder 2",       4,         3,  
    4,           "Coder 3",       3,         5,  
    5,           "Coder 3",       1,         2,  
    8,           "Coder 3",       3,         5,  
    12,          "Coder 3",       4,         4,  
    16,          "Coder 3",       4,         4,  
  )

print("Krippendorff’s Alpha For Participant’s Approach Behaviors")
behavior_data <- dplyr::select(coded_data, content_id, coder_id, behavior)
behavior_data <- pivot_wider(behavior_data, id_cols = coder_id, names_from = content_id, values_from = behavior)
behavior_data <- dplyr::select(behavior_data, -coder_id)
behavior_data <- as.matrix(behavior_data)
kripp.alpha(behavior_data, method = "interval")

print("Krippendorff’s Alpha For Participant’s Self-disclosure")
disclosure_data <- dplyr::select(coded_data, content_id, coder_id, disclosure)
disclosure_data <- pivot_wider(disclosure_data, id_cols = coder_id, names_from = content_id, values_from = disclosure)
disclosure_data <- dplyr::select(disclosure_data, -coder_id)
disclosure_data <- as.matrix(disclosure_data)
kripp.alpha(disclosure_data, method = "interval")

```


